%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{fontawesome}
\usepackage[scale=.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\usepackage{tikz}

\usepackage{mathptmx}
\usepackage[11pt]{moresize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\firstname{Lukasz} % Your first name
\familyname{Malecki} % Your last name

% All information in this block is optional, comment out any lines you don't need


\mobile{+48 537--172--173}
\email{lukasz.malecki@hotmail.com}
\address{Poland}

\extrainfo{
%%  \httplink{https://www.codechef.com/users/priyanka_pps}
\httplink{github.com/vexelenn}
\httplink{linkedin.com/in/llmalecki}
}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% COVER LETTER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\recipient{.}{} % Letter recipient

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\date{\today} % Letter date
\opening{Dear Recruitment Team,}
\closing{Sincerely yours,} % Closing phrase
\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% Print letter title
\makelettertitle{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
My professional experience started in 2010, when during the last months of my studies I started to perform numerical calculations of jet engines(!).
I was also working as a R\&D engineer at the institute, where on top of regular CAD/CAE mechanical designer work I was able to make a couple of publications.
During that time I learned how to perform proper research and I am still leveraging this knowledge within IT sector for example during the process of requirement gathering.
In the IT sector, I become an AWS expert that has a high level of knowledge of serverless infrastructure components and ML solutions.

Currently, I'm working as a Director of Product Management (on a B2B basis).

My current position allowed me to learn how important is tech debt management, and EBITDA prioritization and how good communication can benefit to a remote-based company.
Whenever I see a possibility to optimize work or process I strive to take this route.

Please see some examples:\\
  --- I reorganized the company communication flow to leverage Jira and Slack API automation. Introducing severity 1\&2 path to triage critical tickets. \\
  --- Created a prioritization framework that allows to prioritize top revenue-generating / cost-saving epics using Advanced Roadmap Planner in Jira. \\
  --- Executed international expansion research including risk assessment on how to pick the countries where the international product expansion should be performed. \\

I'm also a very technical person, and my experience concentrates on the AWS stack. I am familiar with a majority of AdTech and MarTech systems (I was designing a lot of them): Data Lakes, DMPs, CDPs, SSPs, DSPs, and Trackers. A big part of my work was also related to Machine Learning (keras, xgb boost, encoding/normalization of data) and many more. \\

I think that my recent experience related to worldwide privacy (Turkey, Brazil, EU, EU Like, California - CPRA, GPP national and state privacy, Japan, South Africa, New Zealand, Canada) as well as deep knowledge of AdTech and MarTech may be in area of your interest. \\

I'm also an IT Geek. During my childhood when my friends were playing computer or PlayStation games, I was playing with new Linux distros and compiling updated kernel versions. I also remember that funny sound before getting online using a cable modem.

When I started to work as a python programmer, I was amazed by Scrum and Agile. Later, I had an opportunity to manage backlogs and drive scrum teams to release multiple projects. Right now I'm working in a company that uses Kanban, which allows for quick prioritization and limits the effort required to conduct meetings from our distributed, remote team.

Happy to hop on a call to chat about the future. \\
Sincerely yours, \\
Lukasz Malecki \\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \makeletterclosing{} % Print letter signature
\textit{I hereby give consent for my personal data included in my application to be processed for the purposes of the recruitment processes under the article 6 paragraph 1 (a) of the Regulation (EU) 2016/679 of the European Parliament and of the Council of 27 April 2016 on the protection of natural persons with regard to the processing of personal data and on the free movement of such data, and repealing Directive 95/46/EC (General Data Protection Regulation).}

\clearpage
\makecvtitle{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{IT Project Based Experience}

\cventry{Director of Product Management}{Data Lake and CDP Platform, ID Resolution}{}{}{}
{\textbf{Objective}: Building a Data Platform integrated with Data Lake and ID Resolution services based on CDN.\\
\textbf{Defining Product Strategy}: Working along with stakeholders across the organization (Engineering, Sales, Product, etc.). Defining and optimizing roadmap.\\
\textbf{Requirements Gathering}: Being involved in market research with sales team to understand complex client/market needs. Managing them into discrete, accurate, and actionable product requirements.\\
\textbf{Supporting Implementation}: In concert with our engineering team, I work to balance speed vs. featureset trade-offs real-time, and ultimately ensure final products satisfy external and internal requirements.\\
\textbf{Driving Product Activation}: Helping to architect go-to-market strategy and product rollouts across the internal sales, marketing, account, and operations teams. Lead the scrum team in using Agile methodology and scrum practices.
}

\cventry{Software Engineer\&Technical PM}{Data Lake and CDP}{}{}{}
{\textbf{Objective}: Building a Customer Data Platform with Data Lake.\\
\textbf{Description}: In this project a Data Lake component was developed to combine and transform multiple data sources.
This component was built using AWS Glue data pipelines and AWS Lake Formation. We almost hit the boundaries of AWS.
Customer Data Platform was a system to create segments and audiences basing on user profile information and behaviour. The CDP part was based in large amount on AWS Neptune --- graph database.
}

\cventry{Technical PM}{DMP system}{}{}{}
{\textbf{Description}: Creating an MVP of Data Management Platform. This system included first and third party data collection and syncing. As an output of the infrastructure, the created audiences were sent to the external DSP.
}

\cventry{Technical PM}{GDPR compliance audit tool}{}{}{}
{\textbf{Objective}: Integration of multiple audit components into one system.\\
\textbf{Description}: The goal of this project was to create an system to perform multiple audit operations on a user configured set of databases. The data verification was intended to detect any GDPR-violation related issues.
}

\cventry{Technical PM}{Traffic Curation platform for SSP}{}{}{}
{\textbf{Objective}: Optimise SSP infrastructure cost by picking valuable traffic.\\
\textbf{Description}: To reach the project objective we were implementing heuristic and machine learning algorithms to verify data patterns and optimise infrastructure cost by selecting valuable traffic.
}

\cventry{Software Engineer\&Technical PM}{Leading research of a ML-based DMP segments}{}{}{}
{\textbf{Objective}: Initial research of a DMP system foundations with ML-based segments.\\
\textbf{Description}: Researching a DMP system with ML-based segments (using for example Click-Through Rate algorithms or other event-based prediction systems). Choosing proper technology and libraries for infrastructure.
}

\cventry{Software Engineer\&Technical PM}{Custom JS enabled video adserver}{}{}{}
{\textbf{Objective}: Building an fully functional custom JS enabled video adserver.\\
\textbf{Description}: The adserver met following IAB requirements: VAST, VPAID. Infrastructure consisted of serverless AWS components (Lambda, API Gateway, Kinesis).
}

\cventry{Python backend developer}{Attribution DSP}{}{}{}
{\textbf{Description}: Maintenance and development of a DSP infrastructure. The system consisted of over 100 EC2 bidder instances, trackers, and orchestration instances. In scope of this project I was involved in development and specification of: bidder cache management, load balancing, specification of new SSP integrations, upgrading OpenRTB versions and more.
}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{FEA \& Mechanical Design Project Based Experience}
% \cventry{Team Leader}{Numerical analysis of a prototype}{}{}{}
% {\textbf{Description}: Managing team in order to conduct numerical analysis of explosive fluid vertical transportation prototype using Lean approach.
% }
% \cventry{Designer\&FEA}{Calculations of stress and strain state inside the rotor of the conventional power plant air heater by provided design \& operational data}{}{}{}{}
% \cventry{Software Engineer}{Creating a software addin for Ansys Mechanical Workbench 13, 14, 15 designed to analyze the strength of welded joints using HOT-Spot European Norms. Debugging \& development by exploring undocumented classes and code}{}{}{}{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\makecvtitle{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional Experience}
\cventry{Apr'21--Present}{Director of Product Management \& Technical Product Manager}{}{}{}{TrueData\\
 --- Reorganizing the company communication flow to leverage Jira and Slack API automation. Introducing severity 1\&2 path to triage tickets.\\
 --- Created a prioritization framework that allows to pick top revenue generating epics using Advanced Roadmap Planner in Jira.\\
 --- Executed an international expansion research including risk assessment on how to pick the countries where the international product expansion should be performed.
}

\cventry{May'17--Apr'21}{Software Engineer \& Technical Project Manager}{}{}{}{Clearcode\\
\textbf{Software Engineering}:\\
 --- Creating Data Flow diagrams based on recent AWS Technology and designing initial architecture\\
 --- Python development, determining KPIs for PoC implementation, execution of PoC and measuring the outcome to pick proper technology\\
\textbf{Collaboration with the customer in the following terms}:\\
 --- Discussing and adjusting the product expectations with the customer with respect to stakeholders' \& customers' needs and other business requirements\\
 --- Synchronizing the Product Backlog items with defined product expectations\\
 \textbf{Collaboration with the development team}:\\
 --- Organizing and conducting scrum events (daily meeting, retrospectives, refinement, sprint review \& planning)\\
 --- Working as a Scrum Master to extend the Agile \& Scrum knowledge in the team. Leading remote workshops and activities to sustain the good culture of remote work
}

\cventry{February'16--May'17}{Python Software Engineer}{}{}{}{Clearcode\\
\textbf{Work Description}: Active development and maintenance of existing OpenRTB based DSP system for US-based customer. The job was to make beautiful code and to get maximum possible performance.
}

\cventry{November'11--February'16}{R\&D}{}{}{}{Central Mining Institute\\
\textbf{Work Description}: Working in the R\&D department of the Institute. Simulating multiple physical phenomena by using open source and proprietary software packages (also based on python). Automating repetitive tasks by using python / open source tools.
}

\cventry{February'11--November'11}{FEA Hot-Spot Programmer (Python/JS)}{}{}{}{MESco\\
\textbf{Work Description}: Creating an application using JavaScript, HTML, and Python to enable FEM analysis and modeling of welded connections for customers. Debugging closed source software.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Technical Skills}
\renewcommand{\listitemsymbol}{-~}
{\small
\cvitem{Mgmt skills}{Optimizing team morale and happiness, Risk assessment, Escalation management, Scrum velocity optimization, Leadership, Requirements gathering}
\cvitem{My Stack}{AWS (Sagemaker, CDK, Glue, Lambda, Fargate, Athena, Neptune, SNS, SQS, CloudWatch, CloudTrail, CloudFormation,), Docker, Docker-compose, git, configuring Bitbucket Pipelines, MLOps, jupyter}
\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}

\cventry{2006--2011}{Master of Science (M.Sc.) in Mechanical Engineering}{}{}{}{The Silesian University of Technology, Gliwice, Poland\\
\textbf{Specialization}: Computer modeling of systems and processes
}

\end{document}
